Healthcare Insights and Sociodemographic Analysis of New York: A Comprehensive Analysis of Patient Records in 2013

### 2023-10-01 STAT405Project.qmd
YAY

grid()
```
<span style="font-size: 14px; font-style: italic;">Figure 4: Trends of Total Charges and Legnth of Stay </span>

@@

```{r}
#| echo: false
ageGroups <- table(cleaned_data$`Age Group`)
barplot(ageGroups,
    main = "Age Group Distribution", xlab = "Age Group",
    ylab = "Frequency", col = "green", border = "black", ylim = c(0, 300000)
)
mtext("Figure 5: Age Group and Distribtion", side = 1, line = 4, adj = -0.1, cex = 0.7, font = 3, col = "black")

@@

heatmap(heatmap_data,
    Rowv = NA,
    Colv = NA,
    col = colorRampPalette(c("white", "blue"))(50),
    xlab = "Gender",
    main = "Gender v. Age Group",
    labRow = row_names,
    labCol = col_names
)
mtext("Figure 6: Gender vs. Age Group Heatmap", side = 1, line = 4, adj = -0.1, cex = 0.7, font = 3, col = "black")

@@

```{r warning = FALSE}
#| echo: false
# install.packages("ggplot2")
ggplot(cleaned_data) +
    aes(x = cleaned_data$"APR Risk of Mortality", y = cleaned_data$"Total Costs", color = "salmon") +
    geom_boxplot() +
    labs(
        title = "Total Costs on Risk of Mortality",
        x = "APR Risk of Mortality", # X-axis title
        y = "Total Costs"
    ) # Y-axis title

@@

```{r warning = FALSE}
#| echo: false
ggplot(cleaned_data, aes(x = `Total Costs`)) +
  geom_density(fill = "blue", alpha = 0.5) +
  facet_grid(`Age Group` ~ .) +
labs(title = "Density Plot of Total Costs per Age-Group Bucket", x = "Total Costs", y = "Density");

```
<span style="font-size: 14px; font-style: italic;">Figure 12: Density Plots of Total Costs per Age-Groups</span>

>>>>

grid()
```
<span style="font-size: 14px; font-style: italic;">Figure 4:Trends of Total Charges and Legnth of Stay </span>

@@

```{r}
#| echo: false
ageGroups <- table(cleaned_data$`Age Group`)
barplot(ageGroups,
    main = "Age Group Distribution", xlab = "Age Group",
    ylab = "Frequency", col = "green", border = "black", ylim = c(0, 300000)
)

@@

heatmap(heatmap_data,
    Rowv = NA,
    Colv = NA,
    col = colorRampPalette(c("white", "blue"))(50),
    xlab = "Gender",
    main = "Gender v. Age Group",
    labRow = row_names,
    labCol = col_names
)

@@

```{r warning = FALSE}
#| echo: false
# install.packages("ggplot2")
ggplot(cleaned_data) +
  aes(x = `APR Risk of Mortality`, y = `Total Costs`) +
  geom_boxplot(color = "salmon") +
  labs(
    title = "Total Costs on Risk of Mortality",
    x = "APR Risk of Mortality",
    y = "Total Costs"
  ) +
  theme_minimal()

@@

```{r warning = FALSE}
#| echo: false
gg <- ggplot(cleaned_data, aes(x = `Total Costs`, y = ..density.., fill = `Age Group`)) +
  geom_density(alpha = 0.5) +
  facet_grid(`Age Group` ~ .) +
  labs(title = "Density Plot of Total Costs per Age-Group Bucket", x = "Total Costs", y = "Density")

gg + scale_y_continuous(labels = scales::number_format(scale = 1e-3)) +
  labs(title = "Density Plot of Total Costs per Age-Group Bucket", x = "Total Costs", y = "Density (in thousands)") +
  theme_minimal()
```
<span style="font-size: 14px; font-style: italic;">Figure 12: Density Plots of Total Costs per Age-Groups</span>
